Selección de Instancias

### 2015-05-04 doc/paper.tex
working paper

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

>>>>

\subsection{Operador}
Ante la necesidad de movernos en el
espacio de busqueda, surge la idea de un operador 
que modifique de manera sutil (y rápida) una solución
dada. 
En nuestro caso, nuestro operador selecciona al
azar un bit ``prendido'' y lo ``apaga'', que se traduce
en ``sacar'' una instancia del conjunto de instancias solución.

De esta manera, se consiguen soluciones cada vez más pequeñas y una tasa
de aciertos $tasa\_clas$ cada vez más precisas: esto viene de si tenemos 
$x$ aciertos y $w$ instancias que no están en la solución, aumetar el tamaño
de una solución conllevaría a una posible $tasa\_clas = x / (w - 1) $,
que supondría una mayor $tasa\_clas$ y por lo tanto una mejor solución. Sin embargo, 
esto no puede estar más alejado de la realidad.
